Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-02-25 xrb2/paper.tex
Updated discussion of flame speed scaling relation

We found in \citet{flame_wave1} that the flame speed, $s$, obeys the following relation:
\begin{equation}
	\label{eqn:flame_speed_scaling}
	s \appropto L_R (\enucdot)^{\half} \propto \frac{(\enucdot)^{\half}}{\Omega},
\end{equation}
where $\enucdot$ is the specific nuclear energy generation rate and $L_R$ is the Rossby length 
described by Equation \ref{eqn:rossby}. This finding was consistent with the results of 
\citet{cavecchi:2013}, who noted that the flame speeds in their simulations scaled with the Rossby 
length. As seen in Figure~\ref{fig:flame_speeds_1}, there is no obvious inverse scaling of the 
flame speed with rotation rate in this set of runs. We observed earlier, however, that nuclear 
reactions progress more quickly at higher rotation rate. This results in a higher 
$\enucdot$ --- up 
to three to four times higher near the burning front after the flame ignites (see Figure 
\ref{fig:maxima}) --- which may counteract the reduction in flame speed from the increased Coriolis 
confinement. We also observe that $\tt{F500}$ accelerates faster than $\tt{F1000}$, which appears 
to experience a small deceleration at early times. This disparity may be a direct result of the 
difference in Coriolis force.

>>>>

\added{For the simple case of a laminar flame front driven by conduction, the propagation rate, 
$s_l$, of the flame is approximately
\begin{equation}
	\label{eqn:laminar_flame_speed}
	s_l \approx \left( \frac{\mathcal{D} \enucdot}{E} \right)^{\half}.
\end{equation}
Here, $\mathcal{D} = k_{th} / (\rho c_v)$ is the thermal diffusivity, $\enucdot$ is the specific
nuclear energy generation rate, and $E$ is the specific total energy \citep{timmeswoosley:1992}. 
\citet{cavecchi:2013} explored the effects of rotation on the flame propagation, and noted that the 
flame speed in their simulations scaled with the ratio $L_R/H_0$ of Rossby length to atmospheric 
scale height. Combining this scaling with Equation \ref{eqn:laminar_flame_speed} yields a revised 
estimate for the flame speed, $s$:
\begin{equation}
	s \approx \frac{L_R}{H_0} s_l \approx \frac{L_R}{H_0} \left( \frac{\mathcal{D} \enucdot}{E} 
	\right)^{\half}.
\end{equation}
Observing that $L_R$ is inversely proportional to the angular rotation frequency $\Omega$ and 
and neglecting variations in $H_0$ and $E$, we can then derive the following approximate scaling 
relation:
\begin{equation}
	\label{eqn:flame_speed_scaling}
	s \appropto \frac{(\mathcal{D} \enucdot)^{\half}}{\Omega}
\end{equation}
We were able to test the validity of this scaling relation in \citet{flame_wave1}, where we studied 
the effects of varying the thermal conductivity/diffusivity, energy generation rate, and rotation 
rate. These results supplemented the findings of \citet{cavecchi:2013}. Despite this formulation of 
the flame speed neglecting some relevant physics (e.g.\ turbulence), the relation proved
consistent with our simulation results.}

\deleted{We found in \citet{flame_wave1} that the flame speed, $s$, obeys the following relation:
$s \appropto L_R (\enucdot)^{\half} \propto \frac{(\enucdot)^{\half}}{\Omega},$
where $\enucdot$ is the specific nuclear energy generation rate and $L_R$ is the Rossby length 
described by Equation \ref{eqn:rossby}. This finding was consistent with the results of 
\citet{cavecchi:2013}, who noted that the flame speeds in their simulations scaled with the Rossby 
length.}

\added{This study explores a more physical parameter space than \citet{flame_wave1}}, and as seen 
in 
Figure~\ref{fig:flame_speeds_1}, there is no clear inverse scaling of the 
flame speed with rotation rate in the new set of runs. We observed earlier, however, that nuclear 
reactions progress more quickly at higher rotation rate. This results in a higher 
$\enucdot$ --- up to three to four times higher near the burning front after the flame ignites (see 
Figure \ref{fig:maxima}) --- which may counteract the reduction in flame speed from the increased 
Coriolis confinement. Comparing accelerations, we also observe that $\tt{F500}$ accelerates faster 
than $\tt{F1000}$, which appears to experience a small deceleration at early times. This disparity 
may be a direct result of the difference in Coriolis force.
